\documentclass[10pt]{article}
\usepackage[a4paper,margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{Aditya More}} \\
    Clemson, South Carolina \\
    \href{mailto:aditya.more@outlook.in}{aditya.more@outlook.in} \quad | \quad 864-765-8212 \\
    \href{https://www.linkedin.com/in/more-aditya}{linkedin.com/in/more-aditya}
\end{center}

\vspace{0.2cm}

\section*{Summary}
Data Scientist and Machine Learning Engineer with a Master’s degree in Computer Science from Clemson University. Experienced in building machine learning systems, developing data-driven models, and applying AI techniques to solve real-world problems. Skilled across the full ML pipeline—from data preprocessing and model development to evaluation and deployment using Python and modern ML frameworks.

\vspace{0.2cm}

\section*{Technical Skills}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Python, SQL
    \item Machine Learning, Deep Learning
    \item Data Visualization, Statistical Modeling
    \item AI Security, MLOps
\end{itemize}

\vspace{0.2cm}

\section*{Experience}

\textbf{Clemson University – School of Computing} \\
\textit{Graduate Student Hourly – Data Science} \hfill Aug 2024 -- Dec 2025
\begin{itemize}[noitemsep, topsep=0pt]
    \item Designed and developed automated lab and homework assignments for a graduate-level Applied Data Science course.
    \item Built Jupyter Notebook-based assignments using Python and nbgrader for automated grading.
    \item Developed exercises across the ML pipeline:
    \begin{itemize}[noitemsep]
        \item Data preprocessing
        \item Outlier detection (IQR, Z-score)
        \item Model selection and cross-validation
        \item Feature selection and PCA
    \end{itemize}
    \item Implemented automated testing logic using Python to validate student submissions.
    \item Created structured notebooks combining explanations, code scaffolding, and evaluation pipelines.
    \item \textbf{Impact:} Streamlined grading and improved learning outcomes through automation.
\end{itemize}

\vspace{0.2cm}

\textbf{Amdocs} \\
\textit{Software Test Engineer} \hfill Oct 2021 -- Dec 2022
\begin{itemize}[noitemsep, topsep=0pt]
    \item Worked on software testing and validation for enterprise applications.
\end{itemize}

\vspace{0.2cm}

\section*{Projects}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed a movie recommendation system using AI-assisted tools and agents.
    \item Evaluated defense mechanisms against jailbreak attacks on large language models.
    \item Replicated adversarial attacks on monocular depth estimation systems.
    \item Built machine learning pipelines for real-world datasets.
\end{itemize}

\vspace{0.2cm}

\section*{Education}
\textbf{Clemson University} \\
Master of Science in Computer Science \hfill Jan 2024 -- Dec 2025

\vspace{0.2cm}

\textbf{D. Y. Patil College of Engineering \& Technology} \\
Bachelor of Engineering in Computer Science \hfill 2017 -- 2021

\vspace{0.2cm}

\section*{Certifications}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Cybersecurity Fundamentals
    \item Certified Information Security and Ethical Hacker (CISEH)
    \item Introduction to Cybersecurity
    \item Data Science Orientation
    \item IBM Blockchain Essentials V2
\end{itemize}

\vspace{0.2cm}

\section*{Languages}
\begin{itemize}[noitemsep, topsep=0pt]
    \item English (Professional)
    \item Hindi (Native/Bilingual)
    \item Marathi (Native/Bilingual)
\end{itemize}

\end{document}