\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.9]{geometry}
\usepackage{fontawesome5}

% Personal Information
\name{Aditya}{More}
\address{Clemson, SC}
\email{aditya.more@outlook.in}
\phone[mobile]{+1~(864)~765~8212}
\social[linkedin]{more-aditya}
\social[github]{Skywalker1910}
\homepage{https://github.com/Skywalker1910/Tech-Portfolio}

\begin{document}
\makecvtitle

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Graduate student in Computer Science (Data Science \& Informatics) at Clemson University. Experienced in machine learning, data analytics, and scalable course development, with hands-on skills in Python, SQL, and cloud computing. Proven record of impact through designing and maintaining online data science curriculum for 200+ students, automating grading with nbgrader, and software testing at scale. Actively seeking \textbf{Data Scientist / ML Engineer / Data Analyst} roles to apply technical and analytical skills to deliver business impact.

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\cventry{Expected Dec 2025}{M.S. Computer Science, Data Science \& Informatics}{Clemson University}{Clemson, SC}{}{}
\cventry{Jul 2021}{B.E. Computer Science \& Engineering}{D Y Patil College of Engineering \& Technology}{Kolhapur, India}{}{}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}
\cventry{Aug 2024 -- Present}{Graduate Student Hourly – School of Computing}{Clemson University}{Clemson, SC}{}{
\begin{itemize}
    \item Designed and developed the online version of Applied Data Science class (Coursera platform).
    \item Created labs and homework assignments covering regression, clustering, PCA, feature selection, and model evaluation.
    \item Automated grading using nbgrader, providing instant student feedback and reducing evaluation time by 50\%.
    \item Maintained all lab/homework notebooks, resolving bugs and improving usability for 200+ students.
    \item Handled technical and course-related tickets on Salesforce, ensuring smooth learner experience.
    \item Conducted 2 weekly office hours to support students with technical and conceptual queries.
\end{itemize}
}

\cventry{Oct 2021 -- Dec 2022}{Software Test Engineer}{Amdocs}{Pune, India}{}{
\begin{itemize}
    \item Conducted end-to-end testing for AT\&T telecom systems across web, video, and retail platforms.
    \item Automated regression \& functional test suites using Postman and Amdocs proprietary tools, improving efficiency.
    \item Collaborated with a 25-member global team across US \& India to deliver seamless system integration.
\end{itemize}
}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Academic Projects}
\cvitem{AdvRM}{Implemented adversarial patches to mislead self-driving car depth estimation systems (graduate security coursework).}
\cvitem{MASTERKEY Jailbreak Replication}{Reproduced jailbreak attempts on GPT-3.5, GPT-4, GPT-4.5; built evaluation metrics to measure model defenses (graduate security coursework).}
\cvitem{Covid-19 Safeguard}{Led a 5-member team to build a real-time surveillance system detecting face masks \& social distancing violations (TensorFlow, OpenCV).}
\cvitem{License Plate Detection}{Built an ANPR system using OpenCV \& Pytesseract to extract license plate numbers from images and video.}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\cvitem{Programming \& ML}{Python, SQL, R, C++, PyTorch, TensorFlow, scikit-learn}
\cvitem{Visualization}{Tableau, Power BI, matplotlib, seaborn}
\cvitem{Cloud \& Tools}{AWS, Git, Docker, Jupyter, nbgrader, Salesforce}
\cvitem{Core Areas}{Machine Learning, Data Analytics, Deep Learning, AI Security}

\end{document}
